---
title: "COASTLOOC data paper"
date: "Last compiled on `r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    highlight: zenburn
    css: "theme.css"
    toc: true
    toc_float:
      collapsed: false
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.pos = "center",
  cache = TRUE
)

library(here)
library(tidyverse)
library(kableExtra)

library(ggpmthemes)
extrafont::loadfonts()
# Set default ggplot2 font size and font family
# devtools::install_github("PMassicotte/ggpmthemes")
theme_set(theme_light_modified(
  base_family = "Montserrat Alternates",
  base_size = 10
))

theme_update(
  panel.border = element_blank(),
  axis.ticks = element_blank(),
  strip.background = element_blank(),
  strip.text = element_text(face = "bold", size = 10, color = "#4c4a4a")
)

source(here("R", "zzz.R"))
```

## Data cleaning and pre-processing

This section shows the main steps that have been applied to pre-process the raw data.

### aCDOM spectra

-   The CDOM spectra were modelled according to the information in @Babin2003.

    -   `acdom` spectra were re-fitted using the complete data (i.e. between 350-500 nm) because the data in `all_abs_transpose.txt` started at 380 nm.

-   Average background values calculated between 683-687 nm and subtracted from each spectrum.

-   Some files were in binary format, so I could not open them (ex.: `C2001000.YSA`).

-   Some spectra start at 300 nm while others at 350 nm.

-   Calculated the correlation between the measured and the fitted values.

    -   Fits with R2 lower than 0.95 were removed from the data.

-   Absorption spectra with any negative values below 500 nm were removed.

-   Exported the complete spectra (350-700 nm): both the raw and the modelled data.

### Phytoplankton and non-algal absorption

-   Absorption spectra with any negative values below 500 nm were removed.

### Irradiance

-   There were negative values in the irradiance data (`Ed`, `Eu`, `Kd`, `Ku`). I have cleaned the data by setting these negative values to `NA`.

This graph shows the number of negative values for Ed by wavelength.

```{r histo_negative_ed}
irradiance <- read_csv(here("data", "clean", "irradiance.csv")) %>%
  filter(ed < 0)

irradiance %>%
  ggplot(aes(x = ed)) +
  geom_histogram() +
  facet_wrap(~ glue::glue("{wavelength} nm"), scales = "free")
```

-   Example of a spectral profile with negative values.

```{r lineplot_negative_ed}
read_csv("data/clean/irradiance.csv") %>%
  filter(station == "C2008000") %>%
  ggplot(aes(x = wavelength, y = ed)) +
  geom_line() +
  geom_point() +
  labs(
    title = "Station C2008000",
    x = "Wavelength (nm)",
    y = parse(text = "E[d](0^'-')~'['~W~m^{-2}~nm^{-1}~']'")
  )
```

-   `Eu` is in fact `Eu0-` that was estimated using a two-exponential function model.

-   `Ed` is in fact `Ed0-` calculated from `0.94 x ed0+`.

- There are differences in wavelengths among cruises. I have not found any information in the report concerning channel change across the missions.

```{r}
irradiance <- read_csv("data/clean/irradiance_negative_values_removed.csv") 

irradiance %>% 
  mutate(cruise = str_sub(station, 1, 2), .after = station) %>% 
  distinct(cruise, wavelength) %>% 
  group_nest(cruise) %>% 
  unnest_wider(data) %>% 
  pivot_wider(names_from = cruise, values_from = wavelength) %>% 
  unnest(everything()) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling()

irradiance %>% 
  mutate(cruise = str_sub(station, 1, 2), .after = station) %>% 
  distinct(cruise, wavelength) %>% 
  group_nest(cruise) %>% 
  unnest_wider(data) %>% 
  pivot_wider(names_from = cruise, values_from = wavelength) %>% 
  unnest(everything()) %>% 
  rowwise() %>% 
  mutate(u  = length(unique(c_across(everything())))) %>% 
  filter(u != 1) %>% 
  select(-u) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling()
```

### Reflectance

-   Reflectance values outside the 0-1 range were set to `NA`.

### AC9

-   Negative values in `a`, `c`, `bp`, `a_dissolved` and `c_dissolved` have been set to `NA`.

-   `a(715)` was used as the baseline, that is why the values are always at 0 (see next graph).

```{r}
knitr::include_graphics(pdf2png(here("graphs", "09_histogram_ac9_negative_values_removed.pdf")))
```

### Other stuff

-   Extracted extra variables (`DOC`, `AQY`) from Massimo 2000.

## Data sampling

Just some graphs to visualize the data. *Note that the same colour palette will be used to represent the areas in all graphics.*

### Temporal sampling

This graph shows when the sampling was performed in the different areas. For instance, we can see that a large fraction of the measurements were made in September of 1998.

```{r}
source(here("R", "zzz.R"))

df <- read_csv(here("data", "clean", "stations.csv"))

df_viz <- df %>%
  mutate(month = clock::date_group(date, "month")) %>%
  count(area, month)

df_viz %>%
  ggplot(aes(x = n, y = factor(month), fill = area)) +
  geom_col() +
  scale_fill_manual(
    breaks = area_breaks,
    values = area_colors
  ) +
  labs(
    x = "Number of observations",
    y = NULL,
    title = "Number of measurements by month"
  ) +
  theme(
    legend.position = "top",
    legend.title = element_blank()
  )
```

### Geographical map

There is a total of 424 different stations were sampled during the COASTLOOC expeditions.

-   Note that there are two stations without geographical coordinates: `C2001000`, `C2002000`.

```{r}
knitr::include_graphics(pdf2png(here("graphs", "02_geographic_map.pdf")))
```

### Bathymetry

I have extracted the bathymetry at each sampling locations. This boxplot provide a general picture of the bathymetry per area. Data from https://download.gebco.net/.

```{r}
knitr::include_graphics(pdf2png(here("graphs", "20_boxplot_bathymetry_by_area.pdf")))
```

### Land-to-sea gradient

We could also present the data in relation with its distance to the land to get an overview of the landscape on optical quantities. For instance, `acdom` will likely be higher for stations located close to the shore because of the terrestrial influence.

```{r, fig.align='center'}
stations <- vroom::vroom(here("data", "clean", "stations.csv"))
distances <- vroom::vroom(here("data", "clean", "distances_to_shore.csv"))

df <- stations %>%
  inner_join(distances)

df %>%
  mutate(area = fct_reorder(area, distance_to_shore_m)) %>%
  ggplot(aes(x = area, y = distance_to_shore_m / 1000, fill = area)) +
  geom_boxplot(size = 0.1, outlier.size = 0.25) +
  scale_y_continuous(labels = scales::label_number_si(accuracy = 0.01)) +
  scale_x_discrete(labels = function(x) str_wrap(x, 10)) +
  scale_fill_manual(
    breaks = area_breaks,
    values = area_colors
  ) +
  labs(
    x = NULL,
    y = "Distance to the land (km)",
    title = "How far are the stations from the land"
  ) +
  theme(
    legend.position = "none"
  )
```

## Available variables

This graph shows an overview of the available variables (excluding radiometric measurements).

```{r}
knitr::include_graphics(pdf2png(
  here("graphs", "06_number_observation_nutrient_by_area.pdf")
))
```

## Absorption measurements

Overview of the averaged absorption spectra for each area.

```{r}
knitr::include_graphics(pdf2png(here(
  "graphs", "11_average_absorption_spectra_by_area.pdf"
)))
```

Comparing `acdom443` for the different areas shows that there is a clear open to coastal gradient.

```{r}
knitr::include_graphics(pdf2png(here(
  "graphs", "13_boxplot_acdom443_by_area.pdf"
)))
```

We can see that the `DOC` follows the same pattern as `acdom443`.

```{r}
knitr::include_graphics(pdf2png(here("graphs", "12_boxplot_doc_by_area.pdf")))
```

We can also use scatter plots to further explore the relationships among variables.

```{r}
knitr::include_graphics(pdf2png(here("graphs", "13_aphy_vs_anap.pdf")))
```

Relationships between some pigments.

```{r}
knitr::include_graphics(pdf2png(here("graphs", "nano_chla_vs_hexanoyloxyfucoxanthin_19.pdf")))
```

### aphy

```{r}
knitr::include_graphics(pdf2png(here("graphs", "04_aphy_spectral_profiles_by_area.pdf")))
```

We could also assess the goodness of the relationships between total chlorophyll-a and phytoplankton absorption for each region.

```{r}
knitr::include_graphics(pdf2png(here("graphs", "15_total_chla_vs_aphy443.pdf")))
```

### anap

```{r}
knitr::include_graphics(pdf2png(here(
  "graphs", "04_anap_spectral_profiles_by_area.pdf"
)))
```

### ap

```{r}
knitr::include_graphics(pdf2png(here(
  "graphs", "04_ap_spectral_profiles_by_area.pdf"
)))
```

### acdom

```{r}
knitr::include_graphics(pdf2png(here(
  "graphs", "04_acdom_spectral_profiles_by_area.pdf"
)))
```

### Absorption partition

In this section I am using the same three stations as in @oubelkheir2007 to explore the additive contributions of each type of absorption.

- For station `C6024000`, `a_p` is lower than `a_cdom` around 400 nm and 550 nm. Should we use this to filter out problematic spectra?

- There are some obvious problems with `a_cdom` measurements. See `C6024000` where there is a bump in absorption around 550 nm.

```{r}
knitr::include_graphics(pdf2png(
  here(
    "graphs",
    "17_absorption_partition_for_three_stations.pdf"
  )
))
```

- This is a ternary plot showing the relative contribution of $a_{\phi}(443)$, $a_{\text{NAP}}(443)$ and $a_{\text{CDOM}}(443)$. I think there are interesting patterns in this graph.

```{r}
knitr::include_graphics(pdf2png(
  here(
    "graphs",
    "19_ternary_plot_absorption.pdf"
  )
))
```

### Spectral slopes

This graph compares the spectral slopes of both `CDOM` and `NAP` absorption spectra.

```{r, fig.align='center'}
s_cdom <- read_csv(here("data", "clean", "s_cdom.csv"))
s_nap <- read_csv(here("data", "clean", "s_nap.csv"))
stations <- read_csv(here("data", "clean", "stations.csv"))

df <- stations %>%
  inner_join(s_cdom, by = "station") %>%
  inner_join(s_nap, by = "station")

df %>%
  select(station, area, s_cdom, s_nap) %>%
  pivot_longer(starts_with("s_")) %>%
  ggplot(aes(x = name, y = value, fill = area)) +
  geom_boxplot(size = 0.1, outlier.size = 0.25) +
  facet_wrap(~area) +
  scale_fill_manual(
    breaks = area_breaks,
    values = area_colors
  ) +
  scale_x_discrete(
    breaks = c("s_cdom", "s_nap"),
    labels = c(parse(text = "S[CDOM]"), parse(text = "S[NAP]"))
  ) +
  labs(
    x = NULL,
    y = quote("Spectral slope" ~ (nm^{
      -1
    }))
  ) +
  theme(
    legend.position = "none"
  )
```

## Irradiance

### Ed

```{r}
knitr::include_graphics(pdf2png(here(
  "graphs", "07_ed_spectral_profiles_by_area.pdf"
)))
```

### Eu

```{r}
knitr::include_graphics(pdf2png(here("graphs", "07_eu_spectral_profiles_by_area.pdf")))
```

### Kd

```{r}
knitr::include_graphics(pdf2png(here("graphs", "07_kd_spectral_profiles_by_area.pdf")))
```

### Ku

```{r}
knitr::include_graphics(pdf2png(here("graphs", "07_ku_spectral_profiles_by_area.pdf")))
```

## Reflectance

```{r}
knitr::include_graphics(pdf2png(here("graphs", "08_reflectance_profiles_by_area.pdf")))
```

## AC9

### Absorption

```{r}
knitr::include_graphics(pdf2png(here("graphs", "09_ac9_a_spectral_profiles_by_area.pdf")))
```

### Beam attenuation

```{r}
knitr::include_graphics(pdf2png(here("graphs", "09_ac9_c_spectral_profiles_by_area.pdf")))
```

### Scattering

```{r}
knitr::include_graphics(pdf2png(here("graphs", "09_ac9_bp_spectral_profiles_by_area.pdf")))
```

## Orientation of the paper

-   The data is a mix of temporal and spatial observations, so how should we present the data?
    
    -   By `area`?

### Journal candidates

-   [Scientific data](https://www.nature.com/sdata/) (I.F: 5.541)
-   [Earth System Science Data (ESSD)](https://earth-system-science-data.net/) (I.F: 9.197)
-   [PLOS One](https://journals.plos.org/plosone/) (I.F: 2.740)

## Figures for the paper

This section shows the figures that I think should be included in the data paper.

### Figure 1

Figure 1: Map of the sampling stations.

```{r fig01}
knitr::include_graphics(pdf2png(here("graphs", "fig01.pdf")))
```

### Figure 2

Figure 2: (**A**) Overview of the temporal sampling for the seven areas. The numbers in the circles indicate the number of visited stations each month. (**B**) Boxplot showing the bathymetry at the sampling locations by area.

```{r fig02}
knitr::include_graphics(pdf2png(here("graphs", "fig02.pdf")))
```

### Figure 3

Figure 3: Total chlorophyll-a (**A**) and particulate organic carbon (**B**) along the inland-to-ocean aquatic continuum.

```{r fig03}
knitr::include_graphics(pdf2png(here("graphs", "fig03.pdf")))
```

### Figure 4

Figure 4: Average total particulate (**A**), non-algal (**B**), phytoplankton (**C**) and chromophoric dissolved organic matter (**D**) absorption spectra in each area.

```{r fig04}
knitr::include_graphics(pdf2png(here("graphs", "fig04.pdf")))
```

## Done

-   [x] Calculate `s_nap` and `s_cdom`. See the method in @Babin2003 where he removes some wavelengths to calculate `s_nap`.

-   [x] Removed dissolved `a` and `c` from the AC9 data because there were problems with the filtering procedure during the sampling.

-   [x] Extract bathymetry at each station.

-   [x] Zoom on geographic areas in Fig. 1 such as figure 13 in the final report.

## Todos

-   No absorption for `Med. Sea (Case 1)`. Is it normal?

-   There are a lot of nutrient parameters that have values of zero. Are they true zero or they indicate missing values?

-   There are wavelength gaps in the `AC9`, `irradiance` and `reflectance` data. Is that normal?

-   Add units to each variable. For example `depth` should becomes `depth_m`.

-   Ternary plot to characterize the contribution of each optically substance to total absorption.

-   True color satellite image to show river plume?

-   I do not have the backscattering data from the BB-4.

-   Some geographical positions are located on land (Adriatic Sea for example).

-   Calculate the apparent visible wavelength index (AVW) and see if it can be exploited in this paper.

-   Wait for Frank to correct the bug with the mrg file where the data columns are not alligned correctly.

## References
